---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview

`"binomial"` is a package specifically designed to provide functions that are able to calculate binomial probabilities and similar measures. The package offers the following functions:  

* `bin_choose()` 
* `bin_probability()`
* `bin_distribution()`
* `plot.bindis()`
* `bin_cumulative()`
* `plot.bincum()`
* `bin_variable()`
* `summary.binvar()`
* `bin_mean()`
* `bin_variance()`
* `bin_mode()`
* `bin_skewness()`
* `bin_kurtosis()`

## Motivation

This package was developed to allow users to easily compute binomial probabilities and plot binomial distributions. The summary measure functions also allow users to quickly compute a measure without having to use any formulas. Other functions like `summary.binvar()` generates neatly formatted output and displays all the important measures.

##  Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 

# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-patrickleihong/Binomial/")

# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-patrickleihong/Binomial/", build_vignettes = TRUE)
```

## Usage

Here is a quick demonstration what each function does:

```{r}
library(binomial)

choose <- bin_choose(n = 5, k = 3)
choose

binprob <- bin_probability(success = 5, trials = 8, prob = 0.5)
binprob

bindist <- bin_distribution(trials = 5, prob = 0.5)
bindist 

bincum <- bin_cumulative(trials = 5, prob = 0.5)
bincum

binvar <- bin_variable(trials = 5, prob = 0.5)
binvar

sumvar <- summary(binvar)
sumvar

mean <- bin_mean(trials = 10, prob = 0.3)
mean

var <- bin_variance(trials = 10, prob = 0.3)
var

mode <- bin_mode(trials = 10, prob = 0.3)
mode

skew <- bin_skewness(trials = 10, prob = 0.3)
skew

kurt <- bin_kurtosis(trials = 10, prob = 0.3)
kurt
```

