---
title: "Getting started with binomial"
author: "Patrick Hong"
date: "May 2, 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial 

The package `"binomial"` contains multiple functions that different outputs related to binomial distributions. It contains functions such as bin_probability that will return the binomial probability after taking in three arguments. There are many summary measure functions that will compute a specific summary measure related to a binomial distribution. These include measures such as mean, variance, mode, skewness, and kurtosis. Finally, there are functions that will return data frames containing the binomial distribution, cumulative distributions, and a function that will return a list containing different summary measures. This document will serve as a tutorial on how to properly use the functions that are included in these functions. 

## Using the `"bin_choose()"` function

Let's start off by learning how to use the `"bin_choose()"` function. The function calculates the number of combinations in which k number of successes can occur in n number of trials. The function takes two arguments: `n` and `k`. `n` is the number of fixed trials and `k` is the number of successes.   
**Note.** `n` must be a non negative number and `k` must be a non negative number that is less than or equal to `n`.  
Examples:

```{r}
choose1 <- bin_choose(n = 5, k = 2)
choose1
choose2 <- bin_choose(n = 5, k = 0)
choose2
```

`k` can also be a vector of length greater than one. 
```{r}
choose3 <- bin_choose(5, 1:3)
choose3
```

## Using the `"bin_probability()"` function

The `"bin_probability"` function builds off the `"bin_choose()"` function. The binomial probability formula is as follows: $$Pr(X = k) = {{n}\choose{k}} \cdot p^k \cdot (1-p)^{n-k}$$. The function takes in 3 arguments: `success (k)`, `trials (n)`, and `prob (p)`. It will then calculate the probability of getting `k` number of successes given `n` number of trials at probability `p`.  
**Note.** `n` must be a non negative number and `k` must be a non negative number that is less than or equal to `n`. `p` is between 0 and 1 (inclusive).  
Examples:
```{r}
bin_prob1 <- bin_probability(success = 2, trials = 5, prob = 0.5)
bin_prob1
bin_prob2 <- bin_probability(success = 0:2, trials = 5, prob = 0.5)
bin_prob2
bin_prob3 <- bin_probability(success = 55, trials = 100, prob = 0.45)
bin_prob3
```

## Using the `"bin_distribution()"` function

The `"bin_distribution()"` function utilizes the `"bin_probability()"` function to compute the binomial probability. It then returns a `"data.frame"` with two classes: the primary class being `bindis` which represents an object of binomial distribution class. The other class is `data.frame` which keeps the object returned as a data frame. The function takes in 2 arguments: `trials` and `prob` and it will generate a data frame that contains 2 columns. The first column is the number of successes and the second column is the probability associated with each number of success.  
Example:
```{r}
bin_distrib <- bin_distribution(trials = 5, prob = 0.5)
bin_distrib

class(bin_distrib)
```

## Using the `"plot.bindis()"` function
The `"plot.bindis()"`function is a plotting method associated with binomial distribution objects, `"bindis"`. This method allows the user to plot the data frame generated by the `"bin_distribution()"` function.  
**Note:** This method only applies to objects of class `bindis`.   
Example:
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

## Using the `"bin_cumulative()"` function
The `"bin_cumulative()"` function utilizes the `"bin_distribution()"`function to return a `"data.frame"` of primary class `"bincum"` which is a binomial cumulative distribution object. The other class is `"data.frame"` to keep the output as a data frame. The `"bin_cumulative()"` builds on the `"bin_distribution()"` by adding an additional column: the data frame returned has 3 columns. The first two columns are successes and its associated probability. The third column is the computed cumulative based on the probabilities.  
Example:
```{r}
bin_cum <- bin_cumulative(trials = 5, prob = 0.5)
bin_cum

class(bin_cum)
```

## Using the `"plot.bincum()"` function
The `"plot.bincum()"` function is a plotting method that is associated with objects of class `"bincum"` or class binomial cumulative distribution. It allows the user to plot the data frame generated by the `"bin.cumulative()"` function.  
**Note:** This method only applies to objects of class `bincum`.  

```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

## Using the `"bin_variable()"` function
The `"bin_variable()"` function takes in 2 arguments: `"trials"` and `"prob"` and returns an object of class `binvar` or a binomial variable object. The function initially creates a list with named elements:   
- trials: number of trials  
- prob: probability of success  
It then invokes the `"print.binvar"` method to print out the output in a better looking format.

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1

class(bin1)
```

## Using the `"summary.binvar()"` function
The `"summary.binvar()"` function is a summary method that utilizes objects of class binomial variable or `binvar`. It is an extension of the `"bin_variable()"` function and will return output as a list of all summary measures along with the named elements printed out in the `"bin_variable()"` function. The returned output will be of class `summary.binvar`. The function will then invoke the `"print.summary.binvar()"` method which will display all the output in a nice format.

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

## Using the functions of measure
The `"binomial"` package comes with 5 summary measure functions:  
1. `"bin_mean()"`  
2. `"bin_variance()"`  
3. `"bin_mode()"`  
4. `"bin_skewness()"`  
5. `"bin_kurtosis()"`  
  
All of these functions take in two arguments: `trials` and `prob` and will return the computed measure respectively.   

Examples:

```{r}
mean <- bin_mean(trials = 10, prob = 0.3)
mean

var <- bin_variance(trials = 10, prob = 0.3)
var

mode <- bin_mode(trials = 10, prob = 0.3)
mode

skew <- bin_skewness(trials = 10, prob = 0.3)
skew

kurt <- bin_kurtosis(trials = 10, prob = 0.3)
kurt

```

